Lab2

### 2021-08-05 src/data/DataCleaning.Rmd
raw unemployed and in_poverty variables mutated

```{r merge limited model dataframe}
d <- merge(x = d_trips, y = d_covid, by = c("fips", "county", "state")) 
d <- merge(x = rural_ind, y = d, by = c("fips"))
d <- merge(x = income_f, y = d, by = c("county"))
d <- merge(x = density_f, y = d, by = c("county"))
d <- d %>% drop_na()

@@

```{r merge model 2 dataframe}
d <- merge(x = unemploy_f, y = d, by = c("county"))
d <- d %>% drop_na()

@@

```{r clean unemployment data}
d <- d %>%
  select(
    county,
    long_trip,
    cases,
    deaths,
    median_income,
    is_rural,
    unemp_rate,
    density,
    pct_lt17,
    pct_gt65,
    povery_rate
  )
knitr::kable(head(d))
```

>>>>

```{r merge limited model dataframe}
d <- merge(x = d_trips, y = d_covid, by = c("fips", "county", "state")) 
d <- merge(x = rural_ind, y = d, by = c("fips"))
d <- merge(x = income_f, y = d, by = c("county"))
d <- d %>% rowwise() %>%
  mutate(
    in_poverty = as.integer(0.01 * povery_rate * total_pop)
  )
d <- merge(x = density_f, y = d, by = c("county"))
d <- d %>% drop_na()

@@

```{r merge model 2 dataframe}
d <- merge(x = unemploy_f, y = d, by = c("county"))
d <- d %>% rowwise() %>%
  mutate(
    unemployed = as.integer(0.01 * unemp_rate * total_pop)
  )
d <- d %>% drop_na()

@@

```{r clean unemployment data}
d <- d %>%
  select(
    county,
    long_trip,
    cases,
    deaths,
    median_income,
    total_pop,
    is_rural,
    unemployed,
    density,
    pct_lt17,
    pct_gt65,
    in_poverty
  )
knitr::kable(head(d))
```
